A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-10-01 paper.tex
Rephrase Evaluations

\section{Introduction}
As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, the data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.

@@

\begin{enumerate}
    \item Generate symmetric keys from the unique device identifier and Message Authentication Code (MAC) of the previous message with Key Derivation Function (KDF). For the first message, the sharing secret initialization information is taken as the MAC of the previous message.\label{item:1}
    \item Compute the MAC of the current message with the Hash-based Message Authentication Code (HMAC) using the symmetric key from \ref{item:1}.
    \item Apply the generated symmetric key to encrypt the plaintext.\label{item:3}
    \item Concatenate the MACs of the current and the previous message, then sign it.\label{item:4}
    \item Send the results of \ref{item:3} and \ref{item:4}.
\end{enumerate}

@@

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription. A discussion of refunds is illustrated.

@@

\section{Evaluations}
\label{section:evaluation}
We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract. 2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.

\subsection{Gas usage of the Product Contract}
We investigate the cost of executing a Product Contract with Ethereum web browser-based IDE Remix. On top of this evaluation, data providers can consider how to set the subscription and brokerage fee to eventually generate profits. The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time. To conquer this condition, we analyze with a fixed range of Gas prices. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. Note that data uploading is only related to MAM operations on the Tangle without transaction fees. Therefore, the Gas estimation only includes trading processes. The high transaction fee for brokers is due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper. Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.

@@

\subsection{MAM Performance Evaluation}
\label{section:mam_performance}
In the following evaluations, all devices run with the IOTA client library instead of IOTA full nodes. MAM is the primary key to resolve all the storage difficulties discussed in previous sections. The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottlenecks in the data subscription platform. In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment. To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. The time duration for each \textit{height} is the average time of running 100 rounds. Since the workflow of channel and endpoint creation are identical, the curves of the same hardware are almost matched. On the other hand, the elapsed time of RPi is grows rapidly when \textit{height} is 5 or above. And the elapsed time of PC remains acceptable even the \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for RPi when data providers need a longer channel/endpoint, which can considered delegating to Accel.
\begin{figure*}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_create}
  \caption{Time cost of MAM creation.}\label{fig:mam_create}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{rpi3_pow}
  \caption{MAM with local PoW \newline vs. MAM with remote PoW \newline vs. Delegated MAM with E2EE}\label{fig:rpi3_pow}  
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{op_share}
  \caption{The percentage each operation takes in total elapsed time.}\label{fig:op_share}  
\endminipage
\end{figure*}

@@

Tips selection requires a stable network connection to wait for the response from IOTA full nodes, and PoW requires enough computation resources to perform. The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has a huge impact. The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority of hardware in the IoT scenarios. Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such a framework. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi. However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
\subsubsection{Experiment}
According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating a channel, these three steps take most of the time to broadcast a MAM message. The result directs a way to improve MAM. Applying remote PoW greatly reduces the elapsed time; hence, the channel creation is the next primary barrier that should be removed. With the adoption of delegated MAM and E2EE, the MAM channel creation would be delegated to Accel, which dramatically enhances the efficiency and makes MAM available for low-level devices. In this way, the performance of delegated MAM stands out from the original MAM one, particularly for different payload sizes. Elapsed time for internet communication and PoW are not included because the steps are the same after sending messages to Accel. Excluding the uniform steps allows us to compare the performance between MAM and delegated MAM clearly. In addition, the MAM channel creation and E2EE asymmetric key pair generation are not counted either, since the two operations are rarely executed. In the E2EE protocol, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.

The steps counted in MAM benchmark including:
\begin{enumerate}
    \item Write key information in the header
    \item Write and encrypt input payload
    \item Publish final message on Tangle
\end{enumerate}

The steps counted in delegated MAM (E2EE) benchmark including:
\begin{enumerate}
    \item Generate symmetric key for encryption
    \item Hash input payload
    \item Encrypt input payload
    \item Transmit final message to Accel
\end{enumerate}

@@

\begin{align}
    y &= 0.0126 x+19.979 \label{lin_mam} \\
    y &= 0.0002 x+9.174 \label{lin_e2ee}
\end{align}

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM, which shows that the previous process is a much more appropriate solution to resource-constrained systems in sending authenticated streaming data. The slope of the E2EE result is much flatter than the result of MAM, which means the former solution can consistently perform in an acceptable time range. In summary, our design enables the resource-constrained hardware to be data providers in the data subscription economy due to the efficiency of the delegated MAM operation and E2EE protocol. The new protocol ensures tamperless data transmission; meanwhile, only authorized subscribers can read the encrypted information.

>>>>

\section{Introduction}
As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care, factories, and vehicles, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, the data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.

@@

\begin{enumerate}
    \item Generate symmetric keys from the unique device identifier and Message Authentication Code (MAC) of the previous message with Key Derivation Function (KDF). For the first message, the sharing secret initialization information is taken as the MAC of the previous message.\label{item:1}
    \item Compute the MAC of the current message with the Hash-based Message Authentication Code (HMAC) using the symmetric key from \ref{item:1}.
    \item Apply the generated symmetric key to encrypt the message.\label{item:3}
    \item Concatenate the MACs of the current and the previous message, then sign it.\label{item:4}
    \item Send the results of \ref{item:3} and \ref{item:4}.
\end{enumerate}

@@

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription and a discussion of refunds is illustrated.

@@

\section{Evaluations}
\label{section:evaluation}
We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) the minimum cost for participants to sustain or subscribe to a data product via Product Contract. 2) the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data providers.

\subsection{Gas usage of the Product Contract}
We investigate the cost of executing a Product Contract with Ethereum web browser-based IDE Remix. On top of this evaluation, data providers can consider how to set the subscription and brokerage fee to eventually generate profits. The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time. To conquer this condition, we analyze with a fixed range of Gas prices. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. Note that data uploading is only related to MAM operations on the Tangle without transaction fees. Therefore, the Gas estimation only includes trading processes. The high transaction fee for brokers is due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper. Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS\cite{Snark} which can generate proofs off-chain and simplify the verification process. It can not only reduce network and storage cost but also improve the privacy and security of encryption keys.

@@

\subsection{MAM Performance Evaluation}
\label{section:mam_performance}
%In the following evaluations, all devices run with the IOTA client library instead of IOTA full nodes.
MAM is the primary component to resolve the storage difficulties discussed in previous sections. The interactions between data providers and MAM can be frequent, hence it is one of the potential bottlenecks during the subscription processes. In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment. A personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.

\subsubsection{Channel / Endpoint Creation}
The length of a channel/endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. The time duration for each \textit{height} is the average time of running 100 rounds. Since the workflow of channel and endpoint creation are identical, the curves of the same hardware almost match. On the other hand, the elapsed time of RPi grow rapidly when \textit{height} is 5 or above. And on PC, all remain acceptable even the \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for data providers, and can be considered delegating to Accel.
\begin{figure*}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_create}
  \caption{Time cost of MAM creation.}\label{fig:mam_create}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{rpi3_pow}
  \caption{MAM with local PoW \newline vs. MAM with remote PoW \newline vs. Delegated MAM with E2EE}\label{fig:rpi3_pow}  
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{op_share}
  \caption{The percentage each operation takes in total elapsed time.}\label{fig:op_share}  
\endminipage
\end{figure*}

@@

Tips selection requires a stable network connection to wait for the response from IOTA full nodes, and PoW requires enough computation resources to perform. The time of RPi distributed widely, from 5 secs to over 2500 secs, due to the randomness of PoW. The simulation results indicate that publishing messages locally is difficult for low-level sensor devices, whereas they are the majority of hardwares in IoT scenarios. Therefore, the devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE, which can lower the threshold to participate the subscription platform. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW, remote PoW and E2EE on RPi. However, improving the performance of MAM is still a direction that worth working on.

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
\subsubsection{Experiment}
From Fig.~\ref{fig:op_share}, send to full node (i.e., prepare and attach the message) and create a channel take most of the time to broadcast a MAM message. In Fig.~\ref{fig:rpi3_pow}, we apply remote PoW to reduce the time of the former, and we delegate MAM to Accel to improve the later. This strategy outperforms the original MAM, particularly for different payload sizes. To better understand the time cost of MAM and delegated MAM, the measurement only contains the MAM operations running on device, where PoW and internet transmission are not included. Furthermore, the MAM channel creation and E2EE asymmetric key pair generation are not included either, since the two operations are rarely executed. In E2EE, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.

The measurement for original MAM includes: 1.) write the key information to the header, 2.) encrypt and write the message, 3.) publish final message to the Tangle. And the measurement for delegated MAM (E2EE) includes: 1.) generate a symmetric key for encryption, 2.) Hash the message, 3.) encrypt the message, 4.) send the message to Accel. The result is shown in Table.~\ref{tab:mam_vs_e2ee}.

@@

The result shows that the elapsed time of E2EE is obviously less than MAM, and E2EE results in a slowly increasing time for different data sizes. This shows that E2EE enables resource-constrained hardwares to join the data subscription economy as providers and ensures tamperless data transmission to Accel.
